Imputation of Missing Values in the Melbourne CBD Pedestrian Dataset

### 2017-08-20 thesis/missing_impute.Rmd
added rmse of test fit for all models

---
title: "Imputation of Missing Values in the Melbourne CBD Pedestrian Dataset"
output:
  html_document:
    theme: united
  html_notebook: default
  pdf_document: default
---
```{r, include=FALSE}
library(plyr)
library(tidyverse)
library(lubridate)
library(magrittr)
library(viridis)
library(gridExtra)
set.seed(12345)
```

@@

# Goodness of Fit
### Visually
```{r, fig.align= 'center', fig.height=24, fig.width=10, fig.retina=1, cache=TRUE, echo=FALSE}
ggplot(filter(test_fitted, Date > "2017-07-23")) +
  geom_line(aes(x = Date_Time, y = Hourly_Counts)) +
  geom_line(aes(x = Date_Time, y = Fitted),
            colour = "violetred2", alpha = 0.75) +
                         facet_wrap(~ Sensor, scales = "free_y", ncol = 4) + theme_minimal() + 
                    theme(axis.text.x = element_text(size = 3),
                          strip.text = element_text(size = 10),
                          axis.text.y = element_text(size = 0)) +
                    xlab("Date") + ylab("Hourly Counts")
```
Looking at plots of actuals (black) against fitted (red) of data from 24 July 2017 to 6 August 2017, we see that some sensors appear to be not operational. We see that there is a mix of very good fitting models and not so good ones. An example of of a reasonably good fitting model is the _Collins Place (North)_ sensor location:
```{r, fig.align= 'center', fig.retina = 1, cache=TRUE}
ggplot(test_fitted %>%
         filter(Date > "2017-07-23",
                Sensor == "Collins Place (North)")) +
      geom_line(aes(x = Date_Time, y = Hourly_Counts)) +
      geom_line(aes(x = Date_Time, y = Fitted), colour = 'violetred2', alpha = 0.7) +
      theme_minimal()
```

@@

>>>>

---
title: "Imputation of Missing Values in the Melbourne CBD Pedestrian Dataset"
output:
  html_document:
    theme: united
  html_notebook: default
  pdf_document: default
---
```{r, include=FALSE}
library(plyr)
library(tidyverse)
library(lubridate)
library(magrittr)
library(viridis)
library(gridExtra)
library(pander)
set.seed(12345)
```

@@

# Goodness of Fit
### Visually
```{r, fig.align= 'center', fig.height=24, fig.width=10, fig.retina=1, cache=TRUE, echo=FALSE}
ggplot(filter(test_fitted, Date > "2017-07-23")) +
  geom_line(aes(x = Date_Time, y = Hourly_Counts)) +
  geom_line(aes(x = Date_Time, y = Fitted),
            colour = "violetred2", alpha = 0.75) +
         facet_wrap(~ Sensor, scales = "free_y", ncol = 4) + theme_minimal() + 
    theme(axis.text.x = element_text(size = 3),
          strip.text = element_text(size = 10),
          axis.text.y = element_text(size = 0)) +
    xlab("Date") + ylab("Hourly Counts") +
    ggtitle("Plot of Actual (black) against Fitted for period 24 July 2017 to 6 August 2017")        
```
Looking at plots of actuals (black) against fitted of data from 24 July 2017 to 6 August 2017, we see that some sensors appear to be not operational. We see that there is a mix of very good fitting models and not so good ones. An example of of a reasonably good fitting model is the _Collins Place (North)_ sensor location:
```{r, fig.align= 'center', fig.retina = 1, cache=TRUE}
ggplot(test_fitted %>%
         filter(Date > "2017-07-23",
                Sensor == "Collins Place (North)")) +
      geom_line(aes(x = Date_Time, y = Hourly_Counts)) +
      geom_line(aes(x = Date_Time, y = Fitted), colour = 'violetred2', alpha = 0.7) +
      theme_minimal()
```

@@

Computing the RMSE for all of the test set (2017 data) for each sensor:

```{r}
test_df <- test_fitted %>% mutate(residsq = (Fitted - Hourly_Counts)^2) %>%
            split(.$Sensor_ID)
test_df_rmse <- data.frame(Sensor_ID = rep(0,43), RMSE = rep(0, 43))
  for (i in 1:43) {
      test_df_rmse$Sensor_ID[i] <- names(test_df)[i]
      test_df_rmse$RMSE[i] <- mean(test_df[[i]]$residsq) %>% sqrt()
  }

test_df_plot <- test_fitted %>% filter(Date > "2017-07-23") %>%
            mutate(residsq = (Fitted - Hourly_Counts)^2) %>%
            split(.$Sensor_ID)
test_df_rmse_plot <- data.frame(Sensor_ID = rep(0,43), RMSE = rep(0, 43))
  for (i in 1:43) {
      test_df_rmse_plot$Sensor_ID[i] <- names(test_df_plot)[i]
      test_df_rmse_plot$RMSE[i] <- mean(test_df_plot[[i]]$residsq) %>% sqrt()
  }
pander(arrange(test_df_rmse, by= RMSE))
```
